Truth space method for caching database queries

### 2015-02-22 english_version/Elsevier/paper_main.tex
Bibliography file in TKDE version was removed. Acknowledgements were added to TODS version.
Conclusion modified: GPU references were removed. Work summarization was added.

\section{Conclusion}
The results obtained will be used in the technology of dynamic building of
multidimensional data. In addition, they are intended to be used with graphic
processors (GPU) to perform the intermediate filtering operations and compound
of different data representations. Researches in this field show that the
operations performed using GPU are much faster than using CPU for small amounts of
data. Performance decreases with increasing amounts of data. The reason is
obvious: as long as the data is put in fast memory of GPU the operations with
them are performed fast. When increasing the amount of data, it is necessary to
move the data to different type of memory, which reduces productivity. However,
GPU
manufacturers are constantly expanding fast memory. At the same time, dimensions
of multidimensional data require relatively small memory, so GPUs are suitable
in solving this problem.

Multidimensional data building systems that use redundant data often face the
problem of updating it. It is often solved by the periodic updating of the
hypercube contents.
A similar method can be used to update the views $P_v$. To reduce the update
time it might be a good practice to use the change log on the database server
and update only those views that have original data changed. However, it should
be noted again that those dimensions don't change often.

>>>>

\section{Conclusion}
The approach suggested in this paper is a theoretical base for a system
interacting with Relational Database. Such system will be capable of defining
cached data availability when executing consecutive queries. This solution is
fresh and wasn't used before. The conditions stated in the theorems don't
require hitting Database to be checked. Results obtained allow us to
analitycally define data missing in cache and query only this data.

The proposed solution will be used in dynamic building of multidimensional data.
Multidimensional data building systems that use redundant data often face the
problem of updating it. It is sometimes solved by the periodic updating of the
hypercube contents.
A similar method can be used to update the views $P_v$. To reduce the update
time it might be a good practice to use the change log on the database server
and update only those views that have original data changed. However, those
dimensions don't change often.

\section{Acknowledgements}
This work is supported by the Russian Foundation for Basic Research under
grant \#12-07-00066-a.
